---
title: "Introduction to binomial package"
author: "Ran Meng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## Calculating probabilities and make plots:
There are 4 main functions that are used to compute the Probability Mass Function(PMF) and display both the probability distributin as well as the cumulative density function in dataframes. 

*bin_choose()* calculates the number of combinations in which k successes can occur in n trials, and this can be achieved by calling the function as demonstrated below. Note that the  *success(k)* argument can also be a vector:

```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 1:3)
```

*bin_probability()*calculates the binomial probability distribution given number of successes, number of trials and the probability of getting a success in one trial:

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

*bin_distribution()* displays probability density of binomial distribution in a dataframe of type *bindis*:
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

We can also plot the dataframe of type *bindis* returned by *bin_distribution()* function:
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

The *bin_cumulative()* function is very similar with *bin_distribution()* as it also returns a dataframe with plotting capability. As the funciton name may suggest, the dataframe has column *cumulative* that contains values of cumulative probabilities:

```{r}
#Displaying dataframe
bin_cumulative(trials = 5, prob = 0.5)

#Plotting
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

## Summary of binomial variables:

In addition to binomial distribution calculations and plots, the package can also convert from variables of other classes to *binvar*, and return summary statistics. 

*bin_variable()* generate a *binvar* object from *trials* and *prob*, which will serve as input for summary description. We can learn about this returned object with *print.binvar()*:

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1 #print.binvar()
```

To get the overview summary description of *binvar*, we can call *summary.binvar()* which takes in the *binvar* object and returns the content of class *summary.binvar*. We can display the content with *print.summary.binvar()*

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)# class of binvar
binsum1 <- summary(bin1) # class of summary.binvar
binsum1 # print.summary.binvar()
```

## Functions of measures

Finally, the package also contains functions that will compute the mean, variance, mode, skewness and kurtosis of a binomial distribution given the number of trials and the probability of success in a single trial. We can get the statistics by calling the corresponding function:

```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
